A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-27 article/04_Discussion.Rmd
language in discussion

This paper is based on ^14^C dates extracted from the Radon-B data set which were prepared for the dating of grave findings. ^14^C data on graves are used to chronologically attach a feature to the absolute chronological context or to better describe the relative development within a finding complex. The questions underlying the creation of a ^14^C date are therefore generally not equivalent to those imposed in this paper. While here the presence of an idea is to be measured abstractly at a certain place at a certain time, graves are usually dated exactly the other way round to contextualize and better understand them as concrete object. By definition, field research is oriented towards small-scale questions that can be answered to their respective extent. It must put a lot of energy into doing justice to all findings that are inevitably destroyed by excavation. There is a fundamental break between that great, theoretical archaeology, which wants to develop comprehensive narratives and only pay quantitative attention to the individual case, and the individual research project or emergency excavation, which has to dedicate a measure of respect and sometimes a lot of working time to each grave. In this thesis, ^14^C data are converted into a proxy of calibrated density distributions within artificial working regions, which is completely detached from the individual context.

@@

The meaning of the data in Radon-B is thus manipulated in at least three ways for the purpose of this work: By concentrating on the dated grave in contrast to the ^14^C date, this work detaches itself from the actual content of the database. By creating artificial time steps and investigation regions, the cultural-historical context of the grave is dissolved. By creating the relative development proxies, the individual grave loses its context. The present paper is therefore a clear secondary use of Radon-B. A better dataset should be grave-related, not date-related, and should contain much more meta-information to each grave.

>>>>

This paper is based on ^14^C dates which were prepared for the dating of graves. There is a fundamental break between that great, theoretical archaeology, which wants to develop comprehensive narratives and only pay quantitative attention to the individual case, and the on-site research or emergency excavation, which has to dedicate a measure of respect and sometimes a lot of time to each grave. In this thesis, ^14^C data are converted into a proxy of calibrated density distributions within artificial working regions, which is completely detached from the individual context. ^14^C data on graves are used to attribute a feature to the absolute chronological context or to better describe the relative development within a site. The questions underlying the creation of a ^14^C date are therefore not equivalent to those imposed in this paper.

@@

The meaning of the data in Radon-B is thus manipulated in at least three ways for the purpose of this work: By concentrating on the dated grave in contrast to the ^14^C date, this work detaches itself from the actual content of the database. By creating artificial time steps and investigation regions, the cultural-historical context of the grave is dissolved. By creating the relative development proxies, the individual grave loses its context. The present paper is a secondary use of Radon-B. A better dataset should be grave-related, not date-related, and should contain much more meta-information for each grave.
